---
title: "Grindstone 100"
author: "Daniel Spakowicz"
date: "8/3/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("rvest")

library(rvest)
library(lubridate)
```

First I'll read in the previous year's results and format the columns.

```{r}
# Grindstone 2016 results page 
# keeps giving 404 error
url <- "http://apps.eco-xsports.com/reports.php?race=1&year=2016"

x <- read.table("grindstone_2016.tsv", sep = "\t", fill = TRUE, header = TRUE)

times <- hms(x$Time)

asmin <- hour(times)*60 + minute(times) + second(times)/60
ashour <- asmin/60
```

```{r}
hist(ashour)
```

In the Laurel Highlands Ultra my percentile finish was just over 30. If I apply that here my predicted finish is 
```{r}
pred_time <- quantile(ashour, 0.317757)
pred_time
```

```{r}
split <- pred_time * 60 / 100
split
```

Dear lord if I shoot for even splits that's 17 min/mile

What time will I reach North River Gap (mile 65.33)? The places where I could pick up Adam are 51, 65 or 81, so I assume he'll want to do 65 and hobble in the last 35 with me.

```{r}
# Pace is in minutes/mile
TimeAtMile<- function(mile, pace) {
  tmp <- mile * pace/60
  t2 <- 18 + tmp - 24
  return(t2)
}

TimeAtMile(65.33, split)
```

```{r}
TimeAtMile(80.35, split)
```

