---
title: "Grindstone 100"
author: "Daniel Spakowicz"
date: "8/3/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# install.packages("rvest")

library(rvest)
library(lubridate)
library(dplyr)
library(readxl)
library(tidyverse)
```

First I'll read in the previous year's results and format the columns.

```{r}
# Grindstone 2016 results page 
# keeps giving 404 error
url <- "http://apps.eco-xsports.com/reports.php?race=1&year=2016"

x <- read.table("../data/grindstone100/grindstone_2016.tsv", sep = "\t", fill = TRUE, header = TRUE)

times <- hms(x$Time)

asmin <- hour(times)*60 + minute(times) + second(times)/60
as.hour <- asmin/60
```

```{r}
hist(as.hour)
abline(v = median(as.hour))
```

In the Laurel Highlands Ultra my percentile finish was just over 30. If I apply that here my predicted finish is 
```{r}
pred_time <- quantile(as.hour, 0.317757)
pred_time
```

```{r}
split <- pred_time * 60 / 100
split
```

Even splits are 17 min/mile.

What time will I reach North River Gap (mile 65.33)? The places where I could pick up Adam are 51, 65 or 81, so I assume he'll want to do 65 and hobble in the last 35 with me.

```{r}
# Pace is in minutes/mile
TimeAtMile <- function(mile, pace) {
  tmp <- mile * pace/60
  t2 <- 18 + tmp - 24
  return(t2)
}

TimeAtMile(65.33, split)
```

```{r}
TimeAtMile(80.35, split)
```

```{r}
TimeAtMile(22.11, split)
```

```{r}
x <- read.table("../data/grindstone100/grindstone-aid-stations.txt", sep = "\t")

header <- c("#", "Aid Station Name", "Location", "Seg Distance", "Mileage", "Crew Access", "Drop Bags", "Record Pace", "20 Hour Time", "Last Runner", "38-Hour Cutoff", "Elevation", "lat", "lng")

names(x) <- header



start.time <- as.POSIXct("2022-09-15 18:00", tz = "EST", format = "%F %R")

time_at_aid <- function(start.time, aid.locations, min.mile) {
  duration <- aid.locations * min.mile
  secs <- round(duration * 60, 0)
  out <- format(start.time + secs, "%H:%M")
  return(out)
}

time_at_aid(start.time = start.time,
            aid.locations = x$`Total Mileage`,
            min.mile = 17.66)
```



# Pacing for different total times

```{r}
getPace <- function(time, total.miles) {
  dec <- as.numeric(time) / total.miles / 60

  secs <- (dec - floor(dec)) * 60

  pace <- ms(paste(floor(dec), secs, sep = ":"))
  
  
  return(pace)  
}

# Goal time
goal30 <- hms("30:00:00")
goal32 <- hms("32:00:00")
cutpace <- hms("38:00:00")

pace.30 <- getPace(goal30, 101.85)
pace.32 <- getPace(goal32, 101.85)
pace.38 <- getPace(cutpace, 101.85)
```

```{r}
x <- 
  x %>%
  mutate("15min/mile pace" = time_at_aid(start.time, x$Mileage, 15),
         "17min/mile pace" = time_at_aid(start.time, x$Mileage, split),
         "17min 40sec"     = time_at_aid(start.time, x$Mileage, 17.6666), 
         "19min/mile pace" = time_at_aid(start.time, x$Mileage, 19),
         "20min/mile pace" = time_at_aid(start.time, x$Mileage, 20)
  )



# Reformat the cutoff column to unify it
x$`38-Hour Cutoff` <- strptime(x$`38-Hour Cutoff`, format = "%I:%M %p")
x$`38 hour cutoff` <- format(x$`38-Hour Cutoff`,"%H:%M")
```


```{r}
goal.pace <- pace.30
distances.vector <- x$Mileage

getGunTime <- function(goal.pace) {
  
  gun.times.df <- data.frame(
    num = as.numeric(goal.pace) * x$Mileage
  )
  
  tmp <- 
    gun.times.df %>%
    mutate(hr.frac = num/60/60,
           hr = floor(hr.frac),
           min = round((hr.frac - hr) * 60),
           min00 = gsub("^(\\d{1})$", "0\\1", min),
           h.m = paste(hr, min00, sep = ":")
           )
  return(tmp$h.m)
}

gun.time <- getGunTime(goal.pace = pace.30)

gun.time
```


```{r}

x <- 
  x %>%
  mutate("30hr.pace" = getGunTime(pace.30),
         "32hr.pace" = getGunTime(pace.32),
         "38hr.pace" = getGunTime(pace.38) 
  )
```


```{r}
# y <- 
#   x %>%
#   select(-c(`#`, `Record Pace`, `lat`, `lng`, `Last Runner`, `20 Hour Time`, `38-Hour Cutoff`))
         
y <- 
  x %>%
  select(`Aid Station Name`, `Seg Distance`, Mileage, `Crew Access`, Elevation, `30hr.pace`, `32hr.pace`, `38hr.pace`)


write.csv(x = y, 
          file = file.path("..", "data", "grindstone100", 
                           paste0(format(Sys.Date(), "%Y"), 
                                  "_grindstone-pacing.csv")
          ),
          row.names = FALSE,
)

```


```{r}
write.csv(x = x, 
          file = file.path("..", "data", "grindstone100", 
                           paste0(format(Sys.Date(), "%Y"), 
                                  "_all-data-for-dad_grindstone.csv")
          ),
          row.names = FALSE,
)
```

```{r}
x <- readxl::read_xlsx("../data/grindstone100/2024_Grinstone100_aid_pacing.xlsx")

header <- c("#", "Aid Station Name", "Total Mileage", "Seg Distance", "Elev. Gain (ft)", "Elev. Loss (ft)", "Cumul. Gain (ft)", "Cumul. Loss (ft)", "Cut-off time",  "Drop Bags", "Crew Access")

names(x) <- header


start.time <- as.POSIXct("2024-09-20 18:00", tz = "EST", format = "%F %R")

time_at_aid <- function(start.time, aid.locations, min.mile) {
  duration <- aid.locations * min.mile
  secs <- round(duration * 60, 0)
  out <- format(start.time + secs, "%H:%M")
  return(out)
}
```



```{r}
y <- 
  x |> 
  mutate("28hr-pace" = time_at_aid(start.time = start.time,
                                   aid.locations = x$`Total Mileage`,
                                   min.mile = 16.16),
         "30hr-pace" = time_at_aid(start.time = start.time,
                                   aid.locations = x$`Total Mileage`,
                                   min.mile = 17.31),
         "32hr-pace" = time_at_aid(start.time = start.time,
                                   aid.locations = x$`Total Mileage`,
                                   min.mile = 18.47),
         "Cut-pace" = time_at_aid(start.time = start.time,
                                   aid.locations = x$`Total Mileage`,
                                   min.mile = 20.77))

```


```{r}
out <- 
  y %>%
  select("#", "Aid Station Name", "Total Mileage", "Seg Distance", "Elev. Gain (ft)", "Elev. Loss (ft)",  "28hr-pace", "30hr-pace", "32hr-pace", "Cut-pace", "Drop Bags", "Crew Access")


write.csv(x = out, 
          file = file.path("..", "data", "grindstone100", 
                           paste0(format(Sys.Date(), "%Y"), 
                                  "_grindstone-pacing.csv")
          ),
          row.names = FALSE
)

```



