---
title: "Mohican 100 Pacing Chart"
author: "Daniel Spakowicz"
date: "6/6/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(lubridate)
library(tidyverse)
library(knitr)
```

I find it comforting to know how I'm doing relative to the cutoff times at all points in the race. If I start feeling lousy I think in terms of how long I have to recover before they kick me out. The Mohican 100 website states that the cutoff is 32 hours; I'd like to know the 32 hour pace at each aid station in cumulative time and time of day. And while I'm at it I'll tweak their spreadsheet of race info a wee bit.

```{r}
cutoff <- as.numeric(hms("32:00:00"))

pace.for.cutoff <- seconds_to_period (cutoff / 100.5 ) %>%
  ceiling

pace.for.cutoff

```

Pace for completion is 19 min 7 seconds per mile. 

If I spend an average of 5 min at each of the 19 aid stations, I would spend

```{r}
min.at.aid <- 5 *  19
min.at.aid
```

95 minutes at aid. After accounting for aid station time my average pace must be:

```{r}
s <- ( cutoff - (min.at.aid * 60) ) / 100.5

seconds_to_period(s) %>%
  ceiling
```

18 min 10 sec per mile. 

```{r}
df <- read.csv("race_data.csv")

cut.pace <- seconds(as.numeric(pace.for.cutoff) * df$Total.Distance) %>%
  seconds_to_period() %>%
  round

cut.pace
```

Reformat cut pace to remove the day period

```{r}
x <- 
  data.frame(total = cut.pace,
             days = day(cut.pace),
             hours = hour(cut.pace),
             minutes = minute(cut.pace),
             seconds = second(cut.pace)) %>%
  mutate(hr.total = days * 24 + hours) %>%
  mutate(total.time = paste(hr.total, minutes, seconds, sep = ":"))
```

Create a time of day for cut pace at all aid stations.

```{r}
start.time <- ymd_hms("2019-06-15 5:00:00")

cut.times <- start.time + cut.pace

cut.time <- format(cut.times, format = "%H:%M")
```

Add in desired clumns to dataframe and remove undesired. 

```{r}
out <- 
  df %>%
  mutate(cut.pace = x$total.time) %>%
  mutate(cut.time = cut.time) %>%
  select(-Aid.Station.Open.Close, -Section.Elevation.Change..ft., -Total.Ascent..ft., -Total.Decent..ft.) %>%
  select(Aid.Station, Section.Distance, Total.Distance, cut.pace, cut.time, Section.Ascent, Section.Decent..ft., Crew.Access, Drop.Bag)

kable(out)
```

```{r}
write.csv(out, "mohican-100_pacing-chart.csv", row.names = FALSE)
```

